int-theory-vacc: Study 2 modeling

### 2019-02-12 notebooks/s2-analysis.Rmd
some refactoring and updated readme

```{r setup, include = F}
library(tidyverse)
library(psych)
# library(ggcorrplot)
library(lme4)
library(brms)
library(rms)
```

@@

```{r tidy, include = F}
# load data
d_all <- read.csv("../data/study2_data.csv")[-1]

# reformat to match previous analyses (i.e., 2 rows per participant)
d_demo <- d_all %>% 
  select(workerId, condition, gender, age, ethnicity, education, job, income,
         political_party, political_beliefs, eligible_pretest, 
         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
         children_youngest_posttest, plan_parent_posttest,
         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
         starts_with("comments"), starts_with("duration"))
d_pre <- d_all %>% 
  select(workerId, ends_with("_pretest")) %>%
  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
            starts_with("attention_"), starts_with("comments"), 
            starts_with("duration"))) %>%
  rename_all(funs(gsub("_pretest", "", .))) %>%
  mutate(phase = "pre")
d_post <- d_all %>% 
  select(workerId, ends_with("_posttest")) %>%
  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
            children_youngest_posttest, plan_parent_posttest,
            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
            starts_with("comments"), starts_with("duration"))) %>%
  rename_all(funs(gsub("_posttest", "", .))) %>%
  mutate(phase = "post")

d <- bind_rows(d_pre, d_post) %>% 
  gather(question, response, -c(workerId, phase)) %>%
  mutate(phase = factor(phase,
                        levels = c("pre", "post")),
         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
         # NOTE: "response" has already been reverse coded!
         question = factor(question),
         scale = factor(gsub("_.*$", "", question),
                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
                                   "vaccStrain", "vaccTox", 
                                   "diseaseSevere", "diseaseRare", 
                                   "infantImmLimCap", "infantImmWeak", 
                                   "medSkept", "hb", "nat", 
                                   "overpar", "parentExpert"))) %>%
  full_join(d_demo) %>%
  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
  filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
  distinct()

# how many left?
d %>% distinct(workerId, condition) %>% count(condition)
```

```{r scores, include = F}
# score all scales
d_scored <- d %>%
  select(workerId, condition, phase, scale, response,
         gender:duration_posttest) %>%
  group_by(workerId, condition, phase, scale) %>%
  mutate(response = as.numeric(response)) %>%
  summarise(mean = mean(response, na.rm = TRUE)) %>%
  ungroup() %>%
  distinct()
```

>>>>

```{r setup, include = F}
library(tidyverse)
library(psych)
# library(ggcorrplot)
library(lme4)
library(brms)
library(rms)

```

@@

```{r tidy, include = F}
# # load data
# d_all <- read.csv("../data/study2_data.csv")[-1]
# 
# # reformat to match previous analyses (i.e., 2 rows per participant)
# d_demo <- d_all %>% 
#   select(workerId, condition, gender, age, ethnicity, education, job, income,
#          political_party, political_beliefs, eligible_pretest, 
#          is_parent_posttest, children_num_posttest, children_oldest_posttest, 
#          children_youngest_posttest, plan_parent_posttest,
#          starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
#          starts_with("comments"), starts_with("duration"))
# d_pre <- d_all %>% 
#   select(workerId, ends_with("_pretest")) %>%
#   select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
#             starts_with("attention_"), starts_with("comments"), 
#             starts_with("duration"))) %>%
#   rename_all(funs(gsub("_pretest", "", .))) %>%
#   mutate(phase = "pre")
# d_post <- d_all %>% 
#   select(workerId, ends_with("_posttest")) %>%
#   select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
#             children_youngest_posttest, plan_parent_posttest,
#             starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
#             starts_with("comments"), starts_with("duration"))) %>%
#   rename_all(funs(gsub("_posttest", "", .))) %>%
#   mutate(phase = "post")
# 
# d <- bind_rows(d_pre, d_post) %>% 
#   gather(question, response, -c(workerId, phase)) %>%
#   mutate(phase = factor(phase,
#                         levels = c("pre", "post")),
#          reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
#          # NOTE: "response" has already been reverse coded!
#          question = factor(question),
#          scale = factor(gsub("_.*$", "", question),
#                         levels = c("vaccIntent", "vaccDanger", "vaccEff", 
#                                    "vaccStrain", "vaccTox", 
#                                    "diseaseSevere", "diseaseRare", 
#                                    "infantImmLimCap", "infantImmWeak", 
#                                    "medSkept", "hb", "nat", 
#                                    "overpar", "parentExpert"))) %>%
#   full_join(d_demo) %>%
#   mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
#   filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
#   distinct()
#

source("../scripts/load-data-s2.R", chdir = TRUE)

# # how many left?
d %>% distinct(workerId, condition) %>% count(condition)
```

```{r scores, include = F}
# score all scales
# d_scored <- d %>%
#   select(workerId, condition, phase, scale, response,
#          gender:duration_posttest) %>%
#   group_by(workerId, condition, phase, scale) %>%
#   mutate(response = as.numeric(response)) %>%
#   summarise(mean = mean(response, na.rm = TRUE)) %>%
#   ungroup() %>%
#   distinct()
```

### 2019-02-12 notebooks/s2-modeling.Rmd
some refactoring and updated readme

source("../study1/vacc_import_data.R", chdir = TRUE)
source("../scripts/gmod_tools.R")
# source("../../Scripts/virtualEvidence.R")

@@

source("../study2/load-study2-data.R", chdir = TRUE)

>>>>

source("../scripts/load-data-s1.R", chdir = TRUE)
source("../scripts/gmod_tools.R")
# source("../../Scripts/virtualEvidence.R")

@@

source("../scripts/load-data-s2.R", chdir = TRUE)
